\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-15 paper/paper.tex
Spelling error
Replace hard-coded references with LaTeX references

Section 2 introduces Elm, signals, state, and the prohibition on signals of
signals. It is targeted to readers familiar with functional programming but not
FRP, and may be skipped by those already comfortable with Elm. Section 3
presents Elm's hover detection for DOM elements, why it initially appears
inadequate, and how it can be extended to meet our needs. Section 4 explains our
menu implementation in detail. Section 5 analyzes TodoFRP. Section 6 concludes
with a notice to the Elm community.

@@

Although it may not appear to be so at first, the result type is a signal of
signals. It is possible to transform the result into \texttt{Signal Signal
(Element, Bool)}. A more mentally convenient type, though impossible to
obtain,\footnote{We explain why in Section 4.}
is \texttt{(Signal Element, Signal Signal Bool)}. There does not exist a general
join function to operate on the \texttt{Signal Signal Bool}.

@@

\section{Conclusion: To the Elm
Community}\label{conclusion-to-the-elm-community}

@@

\subsection{Acknowledgements}\label{acknowledgements}

>>>>

Section \ref{elm-for-functional-programmers} introduces Elm, signals, state, and
the prohibition on signals of signals. It is targeted to readers familiar with
functional programming but not FRP, and may be skipped by those already
comfortable with Elm.
Section \ref{detecting-hover-information} presents Elm's hover detection for DOM
elements, why it initially appears inadequate, and how it can be extended to
meet our needs.
Section \ref{implementing-menus} explains our menu implementation in detail.
Section \ref{related-work-todofrp} analyzes TodoFRP.
Section \ref{conclusion} concludes with a notice to the Elm community.

@@

Although it may not appear to be so at first, the result type is a signal of
signals. It is possible to transform the result into \texttt{Signal Signal
(Element, Bool)}. A more mentally convenient type, though impossible to
obtain,\footnote{We explain why in Section \ref{implementing-menus}.}
is \texttt{(Signal Element, Signal Signal Bool)}. There does not exist a general
join function to operate on the \texttt{Signal Signal Bool}.

@@

\section{Conclusion: To the Elm
Community}\label{conclusion}

@@

\subsection{Acknowledgments}\label{acknowledgments}
